---
title: "linear model from Web"
author: "Angelica Lopez Esparza"
date: "Summer 2023"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS





### scatterplot

```{r}
basicNN <- ggplot(data, aes(y = SIMS, x = ARM)) +
  geom_point() +
  labs(title = "SIMS and ARM") +
  theme(plot.title = element_text(hjust = 0.5))

basicNN
```  
  



### Numerical results
```{r}
cor(SIMS~ARM,data=data)
```
the numerical results for SIMS~ARM IS 0.6860073. This means there is a fair correlation between the two variables of strength.  


### Inferential  (Build model.1)
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
our adjusted r squared is 0.467 and our residual standard error is 1.226. multiple r squared and adjusted r squared are different because the more you put into your model the more the adjusted r squared is affected whereas the multiple r squared will stay the same   



#### Predict at target point
```{r}
mydata<- data.frame(GRIP=88, ARM=104)
predict.lm(model.1, mydata, interval="prediction")
```
the value that it predicted was 1.1579392 but it can go down to a -0.8634158 to an upper 
4.022199  

#### scatterplot with model fit
```{r}
basicNN <- ggplot(data, aes(y = SIMS, x = ARM)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "SIMS ~ ARM") +
  theme(plot.title = element_text(hjust = 0.5))

basicNN

```





## Model 2 SIM~GRIP

### Now add in scatterplot

```{r}
basicNN <- ggplot(data, aes(y = SIMS, x = GRIP)) +
  geom_point() +
  labs(title = "SIMS and GRIP") +
  theme(plot.title = element_text(hjust = 0.5))

basicNN
```

### Numerical results 
```{r}
cor(SIMS~GRIP,data=data)
```
the numerical results for SIMS~GRIP is 0.6398458. SIMS~ARMS has a higher correlation that SIMS~GRIP

### Inferential  (Build model.2)
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
``` 
our adjusted r squared is 0.4053 and our residual standard error is 1.295. comparing the SIMS~GRIP model to the SIMS~ARM model, the SIMS~ARM is the better model  

#### predict model.2 at target point

```{r}
predict.lm(model.2, mydata, interval="prediction")
```
the interval goes from -3.38434 to 1.766475  

#### now add the model fit to our plot for model.2
```{r}
mygrip <- ggplot(data, aes(y = SIMS, x = GRIP)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "SIMS ~ GRIP") +
  theme(plot.title = element_text(hjust = 0.5))

mygrip

``` 


## Model 3 SIM~ARM+GRIP

### Numerical results (cor)
```{r}
cor(SIMS~ARM+GRIP,data=data)
```
the correlation is larger and SIMS~ARM and SIMS~GRIP. with all three together makes a greater correlation of 0.7326545  
  
### Inferential  (Build 2-dimentional model.3)
```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```
our adjusted r squared is 0.5358 and our residual standard error is 1.144. making this model better than the other two. model is SIMS= .037311 * ARM + .0.024470 * GRIP -5.433871  

#### predict model.3 at target point
```{r}
predict.lm(model.3, mydata, interval="prediction")
```  
the interval goes from -1.1716184 to 2.915777  
## Comparing nested models ANOVA Test




### Model.1 vs Model.3
ANOVA(model.1, model.3)
```{r}
anova(model.1, model.3)
```
the p value is .00000499, which does not have any value. it is comparing the residual standard error from model.1   

### Model.2 vs Model.3

## Informally compare Model.1 with model.2

